Advancements in Moltres for Time-Dependent Multiphysics Molten Salt Reactor Modeling

### 2024-12-09 presentation/1d.tex
presentation edits

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: 1-D Neutronics Eigenvalue Simulations}
  \textbf{1-D Neutronics Model Geometries}
  \begin{figure}[htb!]
    \centering
    \includegraphics[width=0.9\columnwidth]{case-geometry}
    \caption{Geometries of the 1-D test cases. The material labeled ``mixture'' represents a
      homogeneous mixture of fuel and graphite at a ratio of 22.5\%-77.5\% by volume. All geometries
      have reflective boundary conditions on the boundary at $x=0$ cm. The right-side boundaries are
      reflective for Cases 1a and 1b, and vacuum for Cases 2a, 2b, 3a, and 3b.}
    \label{fig:case-geom}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: 1-D Neutronics Eigenvalue Simulations}
  \begin{columns}
    \column{5.5cm}
    \textbf{1-D Neutronics Model Setup}
    \vspace{.2cm}

    \begin{itemize}
      \item Material compositions derived from the MSRE design
      \item Reduced gadolinium content in control rod to reduce rod worth from 50000 pcm to 20000 pcm
      \item Eight neutron energy groups
      \item Group constants generated using OpenMC with up to 2nd-order Legendre expansions of scattering
        matrices
      \item Uniform temperature at 900 K
    \end{itemize}
    \column{5.5cm}
    \begin{table}[h]
      \centering
      \caption{Neutron energy group structure in this work. Originally devised by Jaradat
      \cite{jaradat_development_2021-1}.}
      \begin{tabular}{r S}
        \toprule
        Group & {Upper energy bound [eV]} \\
        \midrule
        1 & 2.000$\times 10^7$ \\
        2 & 1.353$\times 10^6$ \\
        3 & 6.734$\times 10^4$ \\
        4 & 9.118$\times 10^3$ \\
        5 & 1.487$\times 10^2$ \\
        6 & 4.000$\times 10^0$ \\
        7 & 6.250$\times 10^{-1}$ \\
        8 & 8.000$\times 10^{-2}$ \\
        \bottomrule
      \end{tabular}
      \label{table:energy-group}
    \end{table}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: 1-D Neutronics Eigenvalue Simulations}
  \textbf{1-D Neutronics Model Numerical Solvers}
  \vspace{.2cm}

@@

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: 1-D Neutronics Eigenvalue Simulations}
  \textbf{1-D Neutronics Model Reactivity Results}
  \begin{figure}[h]
    \centering
    \includegraphics[width=\columnwidth]{rho}
    \caption{Difference in reactivity $\rho$ of all neutronics methods investigated relative
    to OpenMC-CE.}
    \label{fig:1d-rho}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: 1-D Neutronics Eigenvalue Simulations}
  \textbf{1-D Neutronics Model Control Rod Worth Results}
  \begin{figure}[h]
    \centering
    \includegraphics[width=\columnwidth]{worth}
    \caption{Percentage difference in rod worth for Cases 2 and 3 of all neutronics methods
    investigated relative to OpenMC-CE.}
    \label{fig:1d-worth}
  \end{figure}
\end{frame}

\begin{frame}
%  \frametitle{Hybrid $S_N$-Diffusion Method: 1-D Neutronics Eigenvalue Simulations}
  \begin{columns}
    \column{5.5cm}
    \begin{figure}[htb!]
      \centering
      \includegraphics[width=\columnwidth]{case-3a-flux}
      \caption{Case 3a neutron group flux distributions from OpenMC-CE and OpenMC-MG.}
      \label{fig:3a-flux}
    \end{figure}
    \column{5.5cm}
    \begin{figure}[htb!]
      \centering
      \includegraphics[width=\columnwidth]{case-3b-flux}
      \caption{Case 3b neutron group flux distributions from OpenMC-CE and OpenMC-MG.}
      \label{fig:3b-flux}
    \end{figure}
  \end{columns}
\end{frame}

\begin{frame}
%  \frametitle{Hybrid $S_N$-Diffusion Method: 1-D Neutronics Eigenvalue Simulations}
  \begin{columns}
    \column{5.5cm}
    \textbf{Case 3a Neutron Flux Distributions}
    \begin{itemize}
      \item The neutron diffusion and hybrid methods fare worse than the $S_8$ method at capturing
        the oscillatory flux pattern.
      \item The hybrid method performs better than the neutron diffusion method near $x=0$ cm where
        the correction region is situated.
    \end{itemize}
    \column{5.5cm}
    \begin{figure}[htb!]
      \centering
      \includegraphics[width=.975\columnwidth]{case-3a-flux-diff}
      \caption{Absolute difference in neutron group flux distributions for Case 3a from Moltres-$S_8$,
      Moltres-diffusion, Moltres-hybrid, and Python-hybrid relative to OpenMC-MG.}
      \label{fig:3a-flux-diff}
    \end{figure}
  \end{columns}
\end{frame}

\begin{frame}
%  \frametitle{Hybrid $S_N$-Diffusion Method: 1-D Neutronics Eigenvalue Simulations}
  \begin{columns}
    \column{5.5cm}
    \textbf{Case 3b Neutron Flux Distributions}
    \begin{itemize}
      \item The neutron diffusion method performance worsens with the control rod region introduced
        near $x=0$.
    \end{itemize}
    \column{5.5cm}
    \begin{figure}[htb!]
      \centering
      \includegraphics[width=.975\columnwidth]{case-3b-flux-diff}
      \caption{Absolute difference in neutron group flux distributions for Case 3b from Moltres-$S_8$,
      Moltres-diffusion, Moltres-hybrid, and Python-hybrid relative to OpenMC-MG.}
      \label{fig:3b-flux-diff}
    \end{figure}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: 1-D Neutronics Eigenvalue Simulations}
  \textbf{Impact of Correction Subregion Sizes on $k$}
  \begin{itemize}
    \item Minimizing the correction region size is essential for the hybrid method to be
      computationally efficient for time-dependent simulations.
    \item $k$ varies by up to 164 pcm for Case 3a and 109 pcm for Case 3b.
    \item The hybrid method $k$ value does not converge monotonically towards the $S_8$ method $k$ value,
      implying other sources of discrepancies.
  \end{itemize}
  \begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.49\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{correction-size-a-k}
      \caption{Case 3a}
      \label{fig:v1-size-a-k}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{correction-size-b-k}
      \caption{Case 3b}
      \label{fig:v1-size-b-k}
    \end{subfigure}
    \caption{$k_\text{eff}$ estimates from the hybrid method for Cases 3a and 3b with different
    correction subregion sizes. The horizontal lines indicate $k_\text{eff}$ estimates from the
    OpenMC-CE, OpenMC-MG, and $S_8$ methods.}
    \label{fig:v1-size-k}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: 1-D Neutronics Eigenvalue Simulations}
  \textbf{Impact of Correction Subregion Sizes on Rod Worth}
  \begin{itemize}
    \item Rod worth estimates vary non-monotonically with increasing correction subregion size.
    \item Rod worth estimates remain within 0.2 \% of the $S_8$ method rod worth.
    \item The hybrid method produces accurate rod worth estimates as long as the correction region
      size is kept consistent.
  \end{itemize}
  \begin{figure}[htb!]
    \centering
    \includegraphics[width=0.6\columnwidth]{correction-size-rho}
    \caption{Percentage difference in rod worth from the hybrid method relative to OpenMC-CE for
      Cases 3a and 3b with different correction subregion sizes. The horizontal lines indicate
      equivalent rod worth differences from the OpenMC-MG and $S_8$ methods.}
    \label{fig:v1-size-rho}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: 1-D Neutronics Eigenvalue Simulations}
  \textbf{Relaxing the $S_N$ Convergence Tolerance}
  \begin{itemize}
    \item The hybrid $S_N$-diffusion method iteratively couples the neutron diffusion solver with
      the $S_N$ subsolver.
    \item Diffusion-based acceleration schemes for neutron transport methods typically do not
      require the neutron transport calculations to fully converge.
    \item Transport correction parameters tend to converge faster than scalar flux.
    \item Relaxing the $S_N$ subsolver convergence tolerance would provide computational savings to
      the hybrid method.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: 1-D Neutronics Eigenvalue Simulations}
  \begin{columns}
    \column{7cm}
    \textbf{Relaxing the $S_N$ Convergence Tolerance}
    \begin{itemize}
      \item The number of outer iterations generally increases with the $S_8$ convergence tolerance.
      \item The hybrid method exhibits superlinear ($q=1.333$) convergence in $k$ with respect to
        the $S_8$ convergence tolerance value.
    \end{itemize}
    \begin{table}[h]
      \centering
      \caption{Number of outer iterations in hybrid method calculations of Case 3b for a given set of
      convergence tolerance values imposed on the $S_8$ subsolver.}
      \small
      \setlength\tabcolsep{2pt}
      \begin{tabular}{l S S S S S S}
        \toprule
        $S_8$ subsolver tolerance, $\epsilon_\text{tol}$ & {$10^{-8}$} & {$10^{-7}$} & {$10^{-6}$} & {$10^{-5}$} & {$10^{-4}$} & {$10^{-3}$} \\
        \midrule
        Number of outer iterations & 3 & 3 & 3 & 2 & 2 & 1 \\
        \bottomrule
      \end{tabular}
      \label{table:sn-tol}
    \end{table}
    \column{4cm}
    \begin{figure}[h]
      \centering
      \includegraphics[width=\columnwidth]{sn-tol}
      \caption{$k_\text{eff}$ error estimates of Case 3b for a range of convergence tolerance values
      imposed on the $S_8$ subsolver relative to the reference $k_\text{eff}$ value when
      $\epsilon_\text{tol}=10^{-8}$.}
      \label{fig:sn-tol}
    \end{figure}
  \end{columns}
\end{frame}

>>>>

\begin{frame}
  \frametitle{1-D MSRE Neutronics Model Geometries}
  \begin{figure}[htb!]
    \centering
    \includegraphics[width=0.9\columnwidth]{case-geometry}
    \caption{Geometries of the 1-D test cases. The material labeled ``mixture'' represents a
      homogeneous mixture of fuel and graphite at a ratio of 22.5\%-77.5\% by volume. All geometries
      have reflective boundary conditions on the boundary at $x=0$ cm. The right-side boundaries are
      reflective for Cases 1a and 1b, and vacuum for Cases 2a, 2b, 3a, and 3b.}
    \label{fig:case-geom}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{1-D MSRE Neutronics Modeling Approach}
  \begin{columns}
    \column{5.5cm}
    \textbf{1-D Neutronics Model Setup}
    \vspace{.2cm}

    \begin{itemize}
      \item Material compositions derived from the MSRE design
      \item Reduced gadolinium content in control rod to 0.35 wt\%
      \item Eight neutron energy groups
      \item Group constants generated using OpenMC with up to 2nd-order Legendre expansions of scattering
        matrices
      \item Uniform temperature at 900 K
    \end{itemize}
    \column{5.5cm}
    \begin{table}[h]
      \centering
      \caption{Neutron energy group structure in this work. Originally devised by Jaradat
      \cite{jaradat_development_2021-1}.}
      \begin{tabular}{r S}
        \toprule
        Group & {Upper energy bound [eV]} \\
        \midrule
        1 & 2.000$\times 10^7$ \\
        2 & 1.353$\times 10^6$ \\
        3 & 6.734$\times 10^4$ \\
        4 & 9.118$\times 10^3$ \\
        5 & 1.487$\times 10^2$ \\
        6 & 4.000$\times 10^0$ \\
        7 & 6.250$\times 10^{-1}$ \\
        8 & 8.000$\times 10^{-2}$ \\
        \bottomrule
      \end{tabular}
      \label{table:energy-group}
    \end{table}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{1-D MSRE Neutronics Modeling Approach}
  \textbf{1-D Neutronics Model Numerical Solvers}
  \vspace{.2cm}

@@

\begin{frame}
  \frametitle{1-D MSRE Neutronics Simulation Results}
  \textbf{1-D Neutronics Model Reactivity Results}
  \begin{figure}[h]
    \centering
    \includegraphics[width=\columnwidth]{rho}
    \caption{Difference in reactivity $\rho$ of all neutronics methods investigated relative
    to OpenMC-CE.}
    \label{fig:1d-rho}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{1-D MSRE Neutronics Simulation Results}
  \textbf{1-D Neutronics Model Control Rod Worth Results}
  \begin{figure}[h]
    \centering
    \includegraphics[width=\columnwidth]{worth}
    \caption{Percentage difference in rod worth for Cases 2 and 3 of all neutronics methods
    investigated relative to OpenMC-CE.}
    \label{fig:1d-worth}
  \end{figure}
\end{frame}

\begin{frame}
%  \frametitle{Hybrid $S_N$-Diffusion Method: 1-D Neutronics Eigenvalue Simulations}
  \begin{columns}
    \column{5.5cm}
    \textbf{Case 3b Neutron Flux Distributions}
    \begin{itemize}
      \item The neutron diffusion and hybrid methods fare worse than the $S_8$ method at capturing
        the oscillatory flux pattern.
      \item The hybrid method performs better than the neutron diffusion method near $x=0$ cm where
        the control rod is situated.
    \end{itemize}
    \column{5.5cm}
    \begin{figure}[htb!]
      \centering
      \includegraphics[width=.975\columnwidth]{case-3b-flux-diff}
      \caption{Absolute difference in neutron group flux distributions for Case 3b from Moltres-$S_8$,
      Moltres-diffusion, Moltres-hybrid, and Python-hybrid relative to OpenMC-MG.}
      \label{fig:3b-flux-diff}
    \end{figure}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{1-D MSRE Neutronics Simulation Results}
  \textbf{Impact of Correction Subregion Sizes on Rod Worth}
  \begin{itemize}
    \item Rod worth estimates vary non-monotonically with increasing correction subregion size.
    \item Rod worth estimates remain within 0.2 \% of the $S_8$ method rod worth.
    \item The hybrid method produces accurate rod worth estimates as long as the correction region
      size is kept consistent.
  \end{itemize}
  \begin{figure}[htb!]
    \centering
    \includegraphics[width=0.6\columnwidth]{correction-size-rho}
    \caption{Percentage difference in rod worth from the hybrid method relative to OpenMC-CE for
      Cases 3a and 3b with different correction subregion sizes. The horizontal lines indicate
      equivalent rod worth differences from the OpenMC-MG and $S_8$ methods.}
    \label{fig:v1-size-rho}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{1-D MSRE Neutronics Simulation Results}
  \begin{columns}
    \column{7cm}
    \textbf{Relaxing the $S_N$ Convergence Tolerance}
    \begin{itemize}
      \item Transport correction parameters converge faster than scalar flux in the $S_N$ subsolver.
      \item Relaxing the $S_N$ subsolver convergence tolerance would provide computational savings.
      \item The hybrid method exhibits superlinear ($q=1.333$) convergence in $k$ with respect to
        the $S_8$ convergence tolerance value.
    \end{itemize}
    \begin{table}[h]
      \centering
      \caption{Number of outer iterations in hybrid method calculations of Case 3b for a given set of
      convergence tolerance values imposed on the $S_8$ subsolver.}
      \small
      \setlength\tabcolsep{2pt}
      \begin{tabular}{l S S S S S S}
        \toprule
        $S_8$ subsolver tolerance, $\epsilon_\text{tol}$ & {$10^{-8}$} & {$10^{-7}$} & {$10^{-6}$} & {$10^{-5}$} & {$10^{-4}$} & {$10^{-3}$} \\
        \midrule
        Number of outer iterations & 3 & 3 & 3 & 2 & 2 & 1 \\
        \bottomrule
      \end{tabular}
      \label{table:sn-tol}
    \end{table}
    \column{4cm}
    \begin{figure}[h]
      \centering
      \includegraphics[width=\columnwidth]{sn-tol}
      \caption{$k_\text{eff}$ error estimates of Case 3b for a range of convergence tolerance values
      imposed on the $S_8$ subsolver relative to the reference $k_\text{eff}$ value when
      $\epsilon_\text{tol}=10^{-8}$.}
      \label{fig:sn-tol}
    \end{figure}
  \end{columns}
\end{frame}

### 2024-12-09 presentation/2d.tex
slide edits
presentation edits

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: 2-D Neutronics Eigenvalue Simulations}
  \textbf{2-D Neutronics Quarter-Core \& Full-Core MSRE Models}
  \begin{columns}
    \column{5.5cm}
  \begin{figure}[htb!]
    \centering
    \includegraphics[width=\columnwidth]{quarter-core-geom}
    \caption{2-D \gls{MSRE} quarter-core model based on the horizontal cross section of the actual
    \gls{MSRE} geometry.}
    \label{fig:1/4-geom}
  \end{figure}
  \column{5.5cm}
  \begin{figure}[htb!]
    \centering
    \includegraphics[width=\columnwidth]{full-core-geom}
    \caption{2-D \gls{MSRE} full-core model based on the horizontal cross section of the actual
    \gls{MSRE} geometry.}
    \label{fig:full-geom}
  \end{figure}
\end{columns}
\end{frame}

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: 2-D Neutronics Eigenvalue Simulations}
  \begin{columns}
    \column{6.5cm}
    \textbf{2-D Neutronics MSRE Model Setup}
    \vspace{.2cm}

@@

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: 2-D Neutronics Eigenvalue Simulations}
  \textbf{2-D Quarter-Core $k$ \& Rod Worth Results}
  \begin{table}[htb]
    \small
    \centering
    \caption{$k_\text{eff}$ and control rod worth estimates for the 2-D quarter-core \gls{MSRE}
      model. Error values are relative to OpenMC-CE.}
    \setlength\tabcolsep{2pt}
    \begin{tabular}{l S[table-format=1.5(2)] S S[table-format=1.5(2)] S S[table-format=4(2)] S}
      \toprule
      \multirow{2}{*}{Method} & \multicolumn{2}{c}{No Rod} & \multicolumn{2}{c}{Rod} & \multicolumn{2}{c}{Rod worth} \\
                              & {$k_\text{eff}$} & {Error [pcm]} & {$k_\text{eff}$} & {Error [pcm]} & {$\Delta\rho_\text{worth}$ [pcm]} & {Error [pcm]} \\
                              \cmidrule(r){1-1} \cmidrule(rl){2-3} \cmidrule(rl){4-5} \cmidrule(l){6-7}
  	  OpenMC-CE & 1.11209(43) & {-} & 1.01740(42) & {-} & 8370(53) & {-} \\
  	  OpenMC-MG & 1.11979(42) & 618 & 1.02204(41) & 446 & 8541(51) & 172 \\
        Diffusion & 1.12059 & 682 & 1.00903 & -816 & 9867 & 1484 \\
        Hybrid & 1.12174 & 773 & 1.02532 & 760 & 8383 & 13 \\
      \bottomrule
    \end{tabular}
    \label{table:quarter-core}
  \end{table}
  \vspace{.2cm}

  The hybrid method produces accurate rod worth estimates while the neutron diffusion method
      significantly overestimates rod worth.
\end{frame}

\begin{frame}
%  \frametitle{Hybrid $S_N$-Diffusion Method: 2-D Neutronics Eigenvalue Simulations}
%  \textbf{Normalized Fuel Channel Power Distribution}
  \begin{columns}
    \column{6cm}
    \centerline{\textbf{Control Rod Withdrawn}}
  \begin{figure}[p]
    \centering
    \includegraphics[width=\columnwidth]{msre-quarter-no-rod-power}
    \caption{Normalized channel fission rate distribution of the 2-D \gls{MSRE} quarter-core model
    with the rod withdrawn.}
    \label{fig:1/4-no-rod}
  \end{figure}
    \column{6cm}
    \centerline{\textbf{Control Rod Inserted}}
  \begin{figure}[p]
    \centering
    \includegraphics[width=\columnwidth]{msre-quarter-rod-power}
    \caption{Normalized channel fission rate distribution of the 2-D \gls{MSRE} quarter-core model
    with the rod inserted.}
    \label{fig:1/4-rod}
  \end{figure}
\end{columns}
\end{frame}

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: 2-D Neutronics Eigenvalue Simulations}
  \textbf{2-D Quarter-Core Normalized Fuel Channel Power Distribution}
  \begin{table}[htb]
    \small
    \centering
    \caption{Absolute mean and maximum percentage errors in the normalized channel fission rates of
    the 2-D \gls{MSRE} quarter-core models relative to OpenMC. The mean relative standard deviation of
    OpenMC normalized channel fission rates is 0.20\%.}
    \begin{tabular}{l S S S S}
      \toprule
      \multirow{2}{*}{Method} & \multicolumn{2}{c}{No Rod} & \multicolumn{2}{c}{Rod} \\
                              & {Mean [\%]} & {Maximum [\%]} & {Mean [\%]} & {Maximum [\%]} \\
                              \cmidrule(r){1-1} \cmidrule(rl){2-3} \cmidrule(l){4-5}
      Diffusion & 0.40 & 2.63 & 2.01 & 17.44 \\
      Hybrid & 0.40 & 1.32 & 0.43 & 3.08 \\
      \bottomrule
    \end{tabular}
    \label{table:quarter-core-power}
  \end{table}
  \vspace{.2cm}

@@

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: 2-D Neutronics Eigenvalue Simulations}
  \textbf{2-D Full-Core Rod Worth Results}
  \begin{table}[htb]
    \small
    \centering
    \caption{Control rod worth estimates for the 2-D full-core \gls{MSRE} with the
    indicated rods inserted. Error values are relative to OpenMC-CE.}
    \setlength\tabcolsep{2pt}
    \begin{tabular}{l S[table-format=4(2)] S S[table-format=4(2)] S S[table-format=4(2)] S}
      \toprule
      \multirow{2}{*}{Method} & \multicolumn{2}{c}{Rod 1} & \multicolumn{2}{c}{Rod 1 \& 2} & \multicolumn{2}{c}{Rod 1, 2 \& 3} \\
                              & {$\Delta\rho_\text{worth}$ [pcm]} & {Error [pcm]} & {$\Delta\rho_\text{worth}$ [pcm]} & {Error [pcm]} & {$\Delta\rho_\text{worth}$ [pcm]} & {Error [pcm]} \\
                              \cmidrule(r){1-1} \cmidrule(rl){2-3} \cmidrule(rl){4-5} \cmidrule(l){6-7}
      OpenMC-CE & 2450(25) & {-} & 4494(23) & {-} & 6357(24) & {-} \\
      OpenMC-MG & 2523(23) & 73 & 4640(24) & 146 & 6455(22) & 98 \\
      Diffusion & 3019 & 569 & 5439 & 945 & 7519 & 1162 \\
      Hybrid & 2455 & 5 & 4521 & 27 & 6323 & -34 \\
      \bottomrule
    \end{tabular}
    \label{table:full-core-worth}
  \end{table}
  \vspace{.2cm}

  The hybrid method remains effective at improving control rod worth estimates in the full-core
  model.
\end{frame}

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: 2-D Neutronics Eigenvalue Simulations}
  \textbf{2-D Full-Core Normalized Fuel Channel Power Distribution}
  \begin{table}[htb]
    \footnotesize
    \centering
    \caption{Absolute mean and maximum percentage errors in the normalized channel fission rates of
    the 2-D \gls{MSRE} full-core models relative to OpenMC. The mean relative standard deviation of
    OpenMC normalized channel fission rates is 0.27\%.}
    \setlength\tabcolsep{1pt}
    \begin{tabular}{l S S S S S S S S}
      \toprule
      \multirow{2}{*}{Method} & \multicolumn{2}{c}{No Rod} & \multicolumn{2}{c}{Rod 1} & \multicolumn{2}{c}{Rod 1 \& 2} & \multicolumn{2}{c}{Rod 1, 2 \& 3} \\
                              & {Mean [\%]} & {Maximum [\%]} & {Mean [\%]} & {Maximum [\%]} & {Mean [\%]} & {Maximum [\%]} & {Mean [\%]} & {Maximum [\%]} \\
                              \cmidrule(r){1-1} \cmidrule(rl){2-3} \cmidrule(rl){4-5} \cmidrule(rl){6-7} \cmidrule(l){8-9}
      Diffusion & 0.45 & 2.95 & 0.94 & 12.61 & 1.35 & 15.34 & 1.67 & 17.09 \\
      Hybrid & 0.43 & 1.45 & 0.43 & 1.82 & 0.43 & 2.26 & 0.43 & 2.52 \\
      \bottomrule
    \end{tabular}
    \label{table:full-core-power}
  \end{table}
  \vspace{.2cm}

>>>>

\begin{frame}
  \frametitle{2-D Neutronics Quarter-Core \& Full-Core MSRE Models}
  \begin{columns}
    \column{5.5cm}
  \begin{figure}[htb!]
    \centering
    \includegraphics[width=\columnwidth]{quarter-core-geom}
    \caption{2-D \gls{MSRE} quarter-core model based on the horizontal cross section of the actual
    \gls{MSRE} geometry.}
    \label{fig:1/4-geom}
  \end{figure}
  \column{5.5cm}
  \begin{figure}[htb!]
    \centering
    \includegraphics[width=\columnwidth]{full-core-geom}
    \caption{2-D \gls{MSRE} full-core model based on the horizontal cross section of the actual
    \gls{MSRE} geometry.}
    \label{fig:full-geom}
  \end{figure}
\end{columns}
\end{frame}

\begin{frame}
  \frametitle{2-D MSRE Neutronics Modeling Approach}
  \begin{columns}
    \column{6.5cm}
    \textbf{2-D Neutronics MSRE Model Setup}
    \vspace{.2cm}

@@

\begin{frame}
  \frametitle{2-D MSRE Neutronics Simulation Results}
  \textbf{2-D Quarter-Core $k$ \& Rod Worth Results}
  \begin{table}[htb]
    \small
    \centering
    \caption{$k_\text{eff}$ and control rod worth estimates for the 2-D quarter-core \gls{MSRE}
      model. Error values are relative to OpenMC-CE.}
    \setlength\tabcolsep{2pt}
    \begin{tabular}{l S[table-format=1.5(2)] S S[table-format=1.5(2)] S S[table-format=4(2)] S}
      \toprule
      \multirow{2}{*}{Method} & \multicolumn{2}{c}{No Rod} & \multicolumn{2}{c}{Rod} & \multicolumn{2}{c}{Rod worth} \\
                              & {$k_\text{eff}$} & {Error [pcm]} & {$k_\text{eff}$} & {Error [pcm]} & {$\Delta\rho_\text{worth}$ [pcm]} & {Error [pcm]} \\
                              \cmidrule(r){1-1} \cmidrule(rl){2-3} \cmidrule(rl){4-5} \cmidrule(l){6-7}
  	  OpenMC-CE & 1.11209(43) & {-} & 1.01740(42) & {-} & 8370(53) & {-} \\
  	  OpenMC-MG & 1.11979(42) & 618 & 1.02204(41) & 446 & 8541(51) & 172 \\
        Diffusion & 1.12059 & 682 & 1.00903 & -816 & 9867 & 1484 \\
        Hybrid & 1.12174 & 773 & 1.02532 & 760 & 8383 & 13 \\
      \bottomrule
    \end{tabular}
    \label{table:quarter-core}
  \end{table}
  \vspace{.2cm}

  $\Rightarrow$ The hybrid method produces accurate rod worth estimates while the neutron diffusion method
      significantly overestimates rod worth.
\end{frame}

\begin{frame}
%  \frametitle{Hybrid $S_N$-Diffusion Method: 2-D Neutronics Eigenvalue Simulations}
%  \textbf{Normalized Fuel Channel Power Distribution}
  \begin{columns}
    \column{6cm}
    \centerline{\large \textbf{Control Rod Withdrawn}}
  \begin{figure}[p]
    \centering
    \includegraphics[width=\columnwidth]{msre-quarter-no-rod-power}
    \caption{Normalized channel fission rate distribution of the 2-D \gls{MSRE} quarter-core model
    with the rod withdrawn.}
    \label{fig:1/4-no-rod}
  \end{figure}
    \column{6cm}
    \centerline{\large \textbf{Control Rod Inserted}}
  \begin{figure}[p]
    \centering
    \includegraphics[width=\columnwidth]{msre-quarter-rod-power}
    \caption{Normalized channel fission rate distribution of the 2-D \gls{MSRE} quarter-core model
    with the rod inserted.}
    \label{fig:1/4-rod}
  \end{figure}
\end{columns}
\end{frame}

\begin{frame}
  \frametitle{2-D MSRE Neutronics Simulation Results}
  \textbf{2-D Quarter-Core Normalized Fuel Channel Power Distribution}
  \begin{table}[htb]
    \small
    \centering
    \caption{Absolute mean and maximum percentage errors in the normalized channel fission rates of
    the 2-D \gls{MSRE} quarter-core models relative to OpenMC. The mean relative standard deviation of
    OpenMC normalized channel fission rates is 0.20\%.}
    \begin{tabular}{l S S S S}
      \toprule
      \multirow{2}{*}{Method} & \multicolumn{2}{c}{No Rod} & \multicolumn{2}{c}{Rod} \\
                              & {Mean [\%]} & {Maximum [\%]} & {Mean [\%]} & {Maximum [\%]} \\
                              \cmidrule(r){1-1} \cmidrule(rl){2-3} \cmidrule(l){4-5}
      Diffusion & 0.40 & 2.63 & 2.01 & 17.44 \\
      Hybrid & 0.40 & 1.32 & 0.43 & 3.08 \\
      \bottomrule
    \end{tabular}
    \label{table:quarter-core-power}
  \end{table}
  \vspace{.2cm}

@@

\begin{frame}
  \frametitle{2-D MSRE Neutronics Simulation Results}
  \textbf{2-D Full-Core Rod Worth Results}
  \begin{table}[htb]
    \small
    \centering
    \caption{Control rod worth estimates for the 2-D full-core \gls{MSRE} with the
    indicated rods inserted. Error values are relative to OpenMC-CE.}
    \setlength\tabcolsep{2pt}
    \begin{tabular}{l S[table-format=4(2)] S S[table-format=4(2)] S S[table-format=4(2)] S}
      \toprule
      \multirow{2}{*}{Method} & \multicolumn{2}{c}{Rod 1} & \multicolumn{2}{c}{Rod 1 \& 2} & \multicolumn{2}{c}{Rod 1, 2 \& 3} \\
                              & {$\Delta\rho_\text{worth}$ [pcm]} & {Error [pcm]} & {$\Delta\rho_\text{worth}$ [pcm]} & {Error [pcm]} & {$\Delta\rho_\text{worth}$ [pcm]} & {Error [pcm]} \\
                              \cmidrule(r){1-1} \cmidrule(rl){2-3} \cmidrule(rl){4-5} \cmidrule(l){6-7}
      OpenMC-CE & 2450(25) & {-} & 4494(23) & {-} & 6357(24) & {-} \\
      OpenMC-MG & 2523(23) & 73 & 4640(24) & 146 & 6455(22) & 98 \\
      Diffusion & 3019 & 569 & 5439 & 945 & 7519 & 1162 \\
      Hybrid & 2455 & 5 & 4521 & 27 & 6323 & -34 \\
      \bottomrule
    \end{tabular}
    \label{table:full-core-worth}
  \end{table}
  \vspace{.2cm}

  $\Rightarrow$ The hybrid method remains effective at improving control rod worth estimates in the full-core
  model.
\end{frame}

\begin{frame}
  \frametitle{2-D MSRE Neutronics Simulation Results}
  \textbf{2-D Full-Core Normalized Fuel Channel Power Distribution}
  \begin{table}[htb]
    \footnotesize
    \centering
    \caption{Absolute mean and maximum percentage errors in the normalized channel fission rates of
    the 2-D \gls{MSRE} full-core models relative to OpenMC. The mean relative standard deviation of
    OpenMC normalized channel fission rates is 0.27\%.}
    \setlength\tabcolsep{1pt}
    \begin{tabular}{l S S S S S S S S}
      \toprule
      \multirow{2}{*}{Method} & \multicolumn{2}{c}{No Rod} & \multicolumn{2}{c}{Rod 1} & \multicolumn{2}{c}{Rod 1 \& 2} & \multicolumn{2}{c}{Rod 1, 2 \& 3} \\
                              & {Mean [\%]} & {Maximum [\%]} & {Mean [\%]} & {Maximum [\%]} & {Mean [\%]} & {Maximum [\%]} & {Mean [\%]} & {Maximum [\%]} \\
                              \cmidrule(r){1-1} \cmidrule(rl){2-3} \cmidrule(rl){4-5} \cmidrule(rl){6-7} \cmidrule(l){8-9}
      Diffusion & 0.45 & 2.95 & 0.94 & 12.61 & 1.35 & 15.34 & 1.67 & 17.09 \\
      Hybrid & 0.43 & 1.45 & 0.43 & 1.82 & 0.43 & 2.26 & 0.43 & 2.52 \\
      \bottomrule
    \end{tabular}
    \label{table:full-core-power}
  \end{table}
  \vspace{.2cm}
